material and methods

### 2017-09-06 man/ms_1_material_methods.Rmd
update

We computed the values of these indices for tree growth and greenness during each drought event. We considered 2005 and 2012 as singles drought events. The Predrought and Postdrought values of each target variable (i.e.: tree growth or EVI) we computed as the mean value during a period of three years before and after the disturbance events respectively. (:red_circle: Incluir algo de computación de ventana temporal 2,3,4 años: hacerlo tanto en dendro como en EVI)

>>>>

We computed the values of these indices for tree growth and greenness during each drought event. We considered 2005 and 2012 as singles drought events. The predrought and postdrought values of each target variable (i.e.: tree growth or EVI) we computed as the mean value during a period of three years before and after the disturbance events respectively. A period of three years was chosen because we found similar results comparing periods of two, three and four years (:red_circle: incluir tabla de coeficientes y/o gráfica?? como suplement, see Gazol 2017)
